---
title: "The Great Recession 2007-2009"
author: "MuddalakshmiVenkataPrudhvi"
date: "`r Sys.Date()`"

runtime: shiny

output: 
  flexdashboard::flex_dashboard:
      vertical_layout: fill
---

```{r Libraries, include=FALSE, message=FALSE}
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

if (!require("DT")) install.packages("DT")
library(DT)

if (!require("Hmisc")) install.packages("Hmisc")
library(Hmisc)

if (!require("lubridate")) install.packages("lubridate")
library(lubridate)

if (!require("plotly")) install.packages("plotly")
library(plotly)

if (!require("gridExtra")) install.packages("gridExtra")
library(gridExtra)

if (!require("maps")) install.packages("maps")
library(maps)

if (!require("shiny")) install.packages("shiny")
library(shiny)

if (!require("shinydashboard")) install.packages("shinydashboard")
library(shinydashboard)

if (!require("ggridges")) install.packages("ggridges")
library(ggridges)

if (!require("ggplot2")) install.packages("ggplot2")
library(ggplot2)

library(DT)

#install.packages("ggridges")
#library(ggridges)

#library(ggplot2)

```

```{r Global knitr Setup, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(
	#Chunk Code Options
	echo = FALSE, # Show the code in the output
	include = TRUE, # Show the results in the output.
	
	message = FALSE, # messages generated from code are not shown.
	warning = FALSE, # warnings generated from code are not shown.
	
	results = 'asis', # no additional formatting is applied to the results
	comment = NA, 
	
	# don't add the prompt character in R Code, i.e., 
	# don't stop to ask the user for execution
	prompt = FALSE, 	
	
	# # Plot Options - set the width and height (in inches) of all plots generated.
	# fig.height = 6,
	# fig.width = 8,
	# 
	# fig.retina only applies to html output 
	# controls the quality (dpi) of the image.
	fig.retina = 2,
	
	# default alignment of all figures.
	fig.align = 'center'
)

# round all decimals to 4 digits (after the decimal),
# unless specified otherwise in the local options. 
options(digits = 4)

```

```{r load data, include = FALSE, echo=FALSE}

getwd()

setwd("/Users/prudhvi/Desktop/R DATA/R assignment")

load("Snap_Benefits.RMD.RData")
load("UnemploymentRate.RData")
load("PovertyRate.RData")
load("Personal_Income_rates.RData")
load("TotalGDP_rates.RData")
load("Wage_rate.RData")
load("Imp_Exp_Farmtaxes.RData")
load("Income_of_Farm.RData")
load("Agriculture_Loans.RData")
load("Cost_Labor.RData")
load("Personal_Expenditure.RData")
load("Rental_Vacancy_Rates.RData")
load("Mortgage_Value.RData")
load("Housing_Inventory_data.RData")
load("Zillow_homes.RData")
```

# Agriculture Sector

####  
<h2>Agriculture Sector</h2>
Add your analysis / findings / Annotations here.

## Column{data-width=200}
### Select States, Period and Year

```{r SelectState}

selectInput(
	inputId = "StateSelected1",
	label = "Please select the state",
	choices = 
		 Income_Farm%>% 
		select(State) %>% 
		unique()
)

```

Column {data-width=350}
-----------------------------------------------------------------------
### Farm Income
```{r}

Income_Farm %>%
 # filter(State==input$StateSelected1 ) %>%
  gather(-Farm_Income, -State, -Period, key = "var", value = "Year") %>% 
  ggplot(aes(x =  Year, y = Farm_Income, color = Period, shape = factor(Period))) +
    geom_point() +
    facet_wrap(~ State, scales = "free") +
    theme_bw()+
  labs(
      x= "Year",
      y = "Farm Income in Dollars ")

```


### Labor Cost for Agriculture Manufacturing
```{r}
renderPlotly({

cost <- Labor_Cost %>%
  #filter(variable==input$Labor_Cost) %>%
  ggplot( aes(x=Year, y=Labour_cost_share_for_manufacturing, fill=Period))+
   geom_bar(stat="identity", position="dodge") +
  	labs(
      x= "observation_date",
      y = "Agriculture manufacturing cost ")
  
  
ggplotly(cost)

})

```


Column {data-width=350}
-----------------------------------------------------------------------

### Loans to financial Agriculure Production
```{r}
Agriculture_L %>%
  ggplot(aes(x = (Year), y = Loans_to_Finance_Agricultural_Production, fill=Loans_to_Finance_Agricultural_Production)) +
  geom_point(aes(colour = Period)) +
  geom_smooth(se = TRUE) +
  theme_bw()+
  	labs(
      x= "Year",
      y = "Financial Loan Cost in Dollars")

```


### Tax on Farm Imports and Production
```{r}
renderPlot({
	Farm_tax_Imp %>%
	ggplot(aes(x=observation_date, y = `Farm_outputs_Taxes_on_production_and_Imports`))+
	geom_col(aes(fill=`Period`) , alpha=0.6, position = "dodge")+
	geom_path(size=2)+
	geom_point(size=5)+
	geom_smooth(alpha=0.4)+
	geom_line(
		aes( group = `Period`),
		arrow=arrow(ends = "both", type = "closed"))+
	scale_fill_brewer(palette="Paired")+
	labs(
      x= "observation_date",
      y = "Taxes on Imports and Exports")+
	theme(
		plot.title =
			element_text(margin = margin(t = 10, b = 10), size=18),
		legend.position = 'top'
		)

})

```

# Housing Value Index


####  {}
<h2>Housing Value Index</h2>
Add your analysis / findings / Annotations here.

## Column{data-width=200}
### Select States, Period and Year

```{r SelectState1}

selectInput(
	inputId = "StateSelected2",
	label = "Please select the state",
	choices = 
		 Zillow_homes %>% 
		select(State) %>% 
		unique()
)

```



Column {data-width=350}
-----------------------------------------------------------------------
### Zillow home value

```{r}
Zillow_homes %>%
plot_ly(x = ~Year, 
           y= ~Home_Value_Index,
           #  text = paste("Year:", HouseHoldIncome$Year, "Price:",HouseHoldIncome$HouseholdIncomePercent,"Year:", HouseHoldIncome$Period),
             split = (~State),
             type = "scatter",
             mode = "bar") %>%
  add_annotations(
    x= Zillow_homes$Year[which.max(Zillow_homes$Home_Value_Index)],
    y= Zillow_homes$Home_Value_Index[which.max(Zillow_homes$Home_Value_Index)],
    text= "Highest Rate"
  )  %>%
  add_annotations(
    x= Zillow_homes$Year[which.min(Zillow_homes$Home_Value_Index)],
    y= Zillow_homes$Home_Value_Index[which.min(Zillow_homes$Home_Value_Index)],
    text= "Lowest Rate"
  ) %>% layout(title= "Home value Index", font = list(family = 'Arial',size = 8,color = 'rgba(67,67,67,1)'))

```

### Housing Inventory
```{r}
Housing_In <- ggplot(Housing_In, aes(x = Year, y = Housing_Inventory, color = State)) + geom_point(aes(shape = Period,size = Housing_Inventory,frame = Period))
ggplotly(Housing_In)

```
Column {data-width=350}
-----------------------------------------------------------------------

### Rental value rate
```{r}
Rental_Value %>% 
  ggplot(aes(x=Year,y=Rental_Vacancy_rate)) +
  geom_point(alpha=0.5, aes(color=Period,size=0.3)) + 
  labs(x="Year", y= "Rental_Vacancy_rate",
       title="Rental Homes") +
  scale_y_log10()+
  scale_x_log10()+
  geom_smooth(method=lm,se=FALSE)+
  facet_wrap(~State) +
  
  labs(
      x= "Year",
      y = " Rental Vacany Rates in 5 states ")

```


### Mortage Value
```{r}
ggplot(Mortgage_US, aes(x = Year, y = MORTGAGE30US)) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red")+
  facet_wrap(~Period) +
labs(
      x= "Year",
      y = "Mortage Value During the Periods ")

```

# Poverty at a glace


####  {}
<h2>Poverty at a glace</h2>
Add your analysis / findings / Annotations here.

## Column{data-width=200}
### Select States, Period and Year

```{r SelectState2}

selectInput(
	inputId = "StateSelected3",
	label = "Please select the state",
	choices = 
		 TotalWagerate %>% 
		select(State) %>% 
		unique()
)

```




Column {data-width=350}
-----------------------------------------------------------------------
### Unemployment rate
```{r}
ggplot(data = Unemployment_totalRate, aes(x = Year, y = Unemployment)) + 
  geom_point() + 
  theme(plot.background = element_rect(color = "black", # Border color , #State color
                                       size = 1)) +
  facet_grid(State~Period) +
  
labs(
      x= "Year",
      y = "Unemployment Rate ")
```




### Wage rate
```{r}

ggplot(TotalWagerate, aes(x = Year, fill = Period)) +
  geom_density(alpha = 0.5) +
  labs(fill = "Period")+
  facet_grid('State') +
  labs(
      x= "Year",
      y = "Wage Rate ")

```


Column {data-width=350}
-----------------------------------------------------------------------

### GDP
```{r}
renderDT({
 
  Total_GDPrates %>% 
  select(Period, States, Year,
         'GDP in Dollars' = `GDP_in_all_the_industries`)

    
})

```

  
### Estimate poverty rate
```{r}

Povertyrate %>%
  gather(-EstimatePovertyrate, -State, -Period, key = "var", value = "Year") %>% 
  ggplot(aes(x = Year, y = EstimatePovertyrate, color = EstimatePovertyrate, shape = factor(Period))) +
    geom_point() +
    facet_wrap(~ State, scales = "free") +
    theme_bw() +
  labs(
      x= "Year",
      y = "Poverty Rate in Dollars ")

```
     
# Financial Impact


####  {}
<h2>Financial Impact</h2>
Add your analysis / findings / Annotations here.

## Column{data-width=200}
### Select States, Period and Year

```{r SelectState3}

selectInput(
	inputId = "StateSelected4",
	label = "Please select the state",
	choices = 
		 Snap_Benefits %>% 
		select(State) %>% 
		unique()
)

```



Column {data-width=350}
-----------------------------------------------------------------------
### Expenditure sheet 
```{r maps Post}
us_map <- map_data('state')
Expenditure <- PCE %>%
#	filter(Period == "Recession") %>% 
	group_by(State) %>% 
	summarise(
		MeanOwnership = mean(`Personal_Consumption_Expenditures`)
	)

#Convert to lower case.
Expenditure$region <- gsub('_',' ',tolower(Expenditure$State))

merged_data <- left_join(us_map, Expenditure[, c('region', 'MeanOwnership')], by='region')

 
merged_data %>% 
	ggplot()+
	geom_polygon(aes(x=long, y=lat, group=group, fill=MeanOwnership))+
	theme_void()+
   labs(title = 'Personal Expenditure', 
        subtitle = 'By state') +
  labs(
      x= "States",
      y = "Total Expenditure ")

```


### Snap beneits of Receiptents
```{r}
renderPlotly({
gdpPlot <-Snap_Benefits %>% 
 # filter(State==input$stateHouseHold) %>%
  ggplot( aes(x = Year, y= Snap_benefits,  shape=Period)) +
  geom_point(aes(colour = Period), position = "Jitter")+facet_grid(rows= vars(State))+theme_light() +
  labs(title = "SNAP Benefits",
       subtitle = "Snap Benefits of Receiptents",
       caption = "Resources: Fred & Geo Fred dataset")+
 theme_bw(base_size=10)+
  theme(legend.position="right",
        plot.caption=element_text(hjust=0))+
  theme(legend.title = element_text(size=rel(0.5)), legend.text=element_text(size=rel(0.5)), legend.key.size = unit(0.5,"line"),
        axis.title.x = element_text(size = 8), axis.text.x = element_text(size = 5), axis.title.y = element_text(size = 6), axis.text.y = element_text(size=5),
        plot.title = element_text(size = 8, face ="plain"),
        plot.subtitle  = element_text(size = 8, face ="plain"),
        plot.caption = element_text(size = 8, face ="plain"))
ggplotly(gdpPlot)
}) 

```


Column {data-width=350}
-----------------------------------------------------------------------

### Total Personal Income
```{r}
p <- ggplot(data = PersonalIncome_rates, aes(x =Year , y = Personal_Income, color = States)) + geom_point()
p + facet_wrap(~Period, scales = "free") +
  labs(
      x= "Year",
      y = "Personal Income in Dollars ")

```

